---
title: Day 11 of NTRESS 6000
date: October 1, 2024
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

## today we were working on data import, export, and conversion between data types! 

**first things first, we need to load tidyverse** <br>
``` {r,message = FALSE,warning = FALSE}
library(tidyverse)

coronavirus <- read_csv('https://raw.githubusercontent.com/RamiKrispin/coronavirus/master/csv/coronavirus.csv')
```
**we have been working with this coronavirus dataset from [here](https://github.com/owid/covid-19-data)** <br> 
``` {r,message = FALSE}
coronavirus |> 
  filter(cases > 0) |> 
  group_by(date,type) |> 
  summarise(cases=sum(cases)) |> 
  ggplot() + 
  geom_col(aes(date,cases,fill =type))
```

**this is what our data looks like** <br> 
``` {r,message = FALSE}
head(coronavirus)
```

<br> 
**lets filter this raw dataset to keep only the `date`, `country`,`province`,`type`,and `cases` <br> 
we then are piping that dataframe into filter to only keep cases on january 3rd, 2021 

``` {r,message = FALSE}
coronavirus |> 
  select(date,country,province,type,cases) |> 
  filter(date == "2021-01-03")
```

## okay i got too lazy with marking up this file so deal with some dirty code below!! 

``` {r,message = FALSE}
lotr <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/lotr_tidy.csv")
```

``` {r,message = FALSE}
write_csv(lotr, file = "lotr_tidy.csv")

lotr <- read_csv("lotr_tidy.csv")
```


```{r,message = FALSE}
lotr <- read_csv("lotr_tidy.csv", skip = 2)
```



``` {r,message = FALSE}
library(googlesheets4) #install.packages("googlesheets4")

gs4_deauth()
lotr_gs <- read_sheet("https://docs.google.com/spreadsheets/d/1X98JobRtA3JGBFacs_JSjiX-4DPQ0vZYtNl_ozqF6IE/edit#gid=754443596")
```


``` {r,message = FALSE}
#will help turn whatever you have into a number - helpful if your data isnt read as numeric
parse_double("1,23", locale = locale(decimal_mark = ","))
```


``` {r,message = FALSE}
students <- read_csv("https://pos.it/r4ds-students-csv", na = c("","N/A"))
```


``` {r,message = FALSE}
students |> 
  rename(
    student_id = `Student ID`,
    full_name = `Full Name`)
```


``` {r,message = FALSE,warning = FALSE}
library(janitor) #install.packages("janitor")

students |> 
  clean_names(case="lower_upper") |> 
  mutate(
  age = parse_number(ifelse(age == "five", 5, age)))
```

